---
title: "PaperResults"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PaperResults}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, the `gelClust` library is loaded along with a dataset consisting of the TCDD-induced fold change in expression of 932 DEGs across 14 mouse strains and three traits: TCDD burden, change in fat percentage, and change in body weight gain.

```{r setup}
library(gelClust)
data(foldChange)
data(traitData)
```

Then, the number of clusters for signed gamma clustering is selected through maximization of the log-likelihood function. This is chosen in a range from 2 up to the number of samples.

```{r}
gm <- gelMatrix(foldChange)
score <- gammaTest(foldChange, gm, rbound=14)
```

As observed, the optimal number of clusters is 7. We can view these clusters with the `gammaPlot` function.
```{r}
m <- gelSVD(foldChange, 7)
clust <- gammaCluster(gm, m)

set.seed(2)
gammaPlot(gm, clust$labels)
```

Within each of these clusters, we can further obtain sub-clusters such that genes from distinct sub-clusters within the same primary cluster are uncorrelated after controlling for the cluster itself.
```{r}
sub.clust <- subClusters(foldChange, clust, 10)
table(sub.clust$labels)
```


